\documentclass[10pt,a4paper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{amssymb}
\address{
\rightline{	Shenren Xu, PhD}\\
%\rightline{ Yangtze River Delta Research Institute of NPU}\\
\rightline{Northwestern Polytechnical University}\\
\rightline{Xi'an, Shaan~P.R.~China}\\
\rightline{Email: shenren\_xu@nwpu.edu.cn} }
\signature{Regards,\\Shenren Xu} 

\begin{document} 
	\begin{letter}{}
		
			\opening{Dear reviewers,\\
				~\\
				Thank you all for kindly reviewing our work and
				for providing feedback on our initial manuscript. We have
				careful read the comments and updated our paper
				accordingly. The changes we have made are listed below.
				\begin{itemize}					
					\item We added the reference for the
					experimental results on the laminar flow
					around cylinder on page 7;
					\item on page 8, section 3,``Arpack'' is now capitalized;
					\item In page 11, the last sentence in the first paragraph, why has no mesh convergence study been performed?\\
					Re: it was not performed as there was not enough time for such 
					thorough numerical experiment. This sentence is now removed to avoid confusion;
					\item Which operation point is used for Fig.8? The most left point?
				\\
				Re: the contour plot is done for the left-most data point on the
				whole-annulus performance curve. This is now clearly stated in the text;	
				\item In page 11, in the first sentence, ``one'' should be when.\\
				Re: this is now corrected.
				\end{itemize}		
				 We hope that our revised paper is answering the questions
				 of the reviewers. Thank you again for your time reviewing our work.}

		

		\closing{~} 
		%\cc{Cclist} 
		%\ps{adding a postscript} 
		%\encl{list of enclosed material} 
	\end{letter} 
\end{document}